Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-08 summary.tex
my compilation problem

Our linear axisymmetric analysis of the VSI 
considers (uniquely to our knowledge) finite cooling times in a vertically global model.  
Our main analytical finding, which we confirm numerically, is the critical cooling 
timescale above which VSI growth is suppressed, Eqs.\ \ref{prelim_bcrit} and {iso_vsi_cond}.
Short cooling times are needed to weaken the stabilizing effects of vertical buoyancy, thereby allowing 
the free energy in vertical shear to drive instability.

>>>>

Our linear axisymmetric analysis of the VSI 
considers (uniquely to our knowledge) finite cooling times in a vertically global model.  
Our main analytical finding, which we confirm numerically, is the critical cooling 
timescale above which VSI growth is suppressed, Eqs.\ \ref{prelim_bcrit} and \ref{iso_vsi_cond}.
Short cooling times are needed to weaken the stabilizing effects of vertical buoyancy, thereby allowing 
the free energy in vertical shear to drive instability.
